---
date: "`r format(Sys.Date(), format = '%d %b %Y')`"
output:
  html_document:
    keep_md: yes
---

rawr
====

personal package with miscellaneous functions, stuff in progress, and tools I use regularly

to install:

```r
# install.packages('devtools')
devtools::install_github('raredd/rawr')
```

**some useful things for ...**

```{r, echo=FALSE}
library('rawr')

options(width = 100)

library('knitr')
opts_chunk$set(fig.width = 10, fig.height = 8)
```

### survival analysis

```{r}
library('survival')
s <- survfit(Surv(time, status) ~ factor(ph.ecog), cancer)

## kaplan-meier with a whole bunch of extra junk
kmplot(
  s,
  atrisk.col = TRUE, strata.lab = TRUE,
  median = TRUE, hr_text = TRUE, pw_test = TRUE
)

## convenience function for survival analysis
kmplot_by(
  'factor(ph.ecog)', time = 'time', event = 'status', cancer,
  tt_test = TRUE, by = 'sex', strata_lab = FALSE, atrisk.type = 'survival',
  atrisk.col = TRUE, median = TRUE, hr_text = TRUE, pw_test = TRUE
)

## get the pairwise differences easily
survdiff_pairs(s)
```

### misc plots

**box plot + violin plot + dot plot + testing + ...**

```{r}
tplot(
  mpg ~ vs + gear, mtcars, test = TRUE,
  type = c('dv', 'v', 'd', 'db', 'b', 'd'),
  quantiles = c(0.25, 0.5, 0.75), lwd = c(1, 2.5, 1)
)
```

**heatmap + row/column matrices + formatting**

```{r}
x <- scale(as.matrix(mtcars))

rc <- cbind(gear = x[, 'gear'], am = x[, 'am'], vs = x[, 'vs'])
rc[] <- palette()[rc + 2L]

cc <- rbind(var1 = nchar(colnames(x)), var2 = nchar(sort(colnames(x))))
cc[] <- palette()[cc]

heatmap.3(
  x, scale = 'column', distfun = 'spearman', hclustfun = 'ward.D2',
  RowSideColors = rc, ColSideColors = cc,
  labRowCol = rc[, 3], labColCol = cc[1, ],
  margins = c(5, 10),
  colsep = c(2, 6), rowsep = c(9, 14, 21), sepwidth = c(5, 2)
)
```

### stat things

**tests for doubly- (jonckheere-terpstra) or singly-ordered (kruskal-wallis) tables**

```{r}
tbl <- table(mtcars$gear, mtcars$cyl)
# fisher.test(tbl)
jt.test(tbl)

kw.test(tbl, simulate.p.value = TRUE)
```

**test for _ordered_ kruskal-wallis rank-sum**

```{r}
# kruskal.test(mpg ~ cyl, mtcars)
cuzick.test(mpg ~ cyl, mtcars)
```

### knitr/convenience things

**basically a table**

```{r}
tabler_by2(
  mtcars, c('gear', 'vs'), 'cyl',
  stratvar = 'am', n = table(mtcars$am),
  zeros = '-', pct = TRUE, pct.total = TRUE
)
```

**basically a table**

```{r}
tabler_stat2(
  within(mtcars, cyl <- factor(cyl, ordered = TRUE)),
  c('Miles/gal' = 'mpg', 'Engine (V/S)' = 'vs', Cylinders = 'cyl'),
  c('# of gears' = 'gear'), correct = 'BH',
  htmlArgs = list(caption = 'Table 1.')
)
```

**a table, basically**

```{r}
set.seed(1)
r <- c('CR', 'PR', 'SD', 'PD', 'NE')
x <- factor(sample(r, 30, replace = TRUE), r)

table(x)
t(t(tabler_resp(x, 3:1)))
```

**in-line convenience functions**

```{r}
intr(mtcars$mpg)
intr(mtcars$mpg, conf = 0.95)

countr(mtcars$cyl)
countr(table(mtcars$vs))
```
